---
title: "Nutrimeter: A Tentative User-Manual"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Nutrimeter_Vignette}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```


## What can I do with Nutrimeter?

With Nutrimeter you can track your daily intake of the most important vitamins and minerals. You can log the foods you ate into a food diary and see how much percent of the RDA (Recommended Daily Allowance) you have consumed of each nutrient so far.

## How do I use Nutrimeter?
First, install the package and access it from the `library()`.

```{r setup, eval = F}
install.packages("NutriMeter")
library(NutriMeter)
```

First, enter your age and gender. These two variables are used to determine how much of each nutrient you need per day. NutriMeter uses the Recommended Daily Allowances (RDA) from the US National Institutes of Health. For more information, [click here](https://ods.od.nih.gov/HealthInformation/dailyvalues.aspx).

** *screenshot will be inserted here* **

Next, you can look up a food you have consumed in our database. You should add the amount you have consumed of it with the correct unit. For example, if you ate one apple that weighed 250 grams, you can add it to your food diary like this:

** *screenshot will be inserted here* **

After each entry you should click submit. Then you can see an overview (see screenshot below of your food diary of the day and below this, progress bars that show you how much % of each nutrient RDA you already reached for the day.

** *screenshot will be inserted here* **


## Vitamins & Minerals Cheatsheet

This cheatsheet includes all vitamins and minerals you can track with Nutrimeter. Have a look what each nutrient is important for and what some good sources are.

#### Vitamin A
- **Important for:**
  * immune system
  * skin
  * vision
- **Sources:**
  * orange and yellow fruits and vegetables (e.g., oranges, carrots)
  * green leafy vegetables (e.g., spinach, peas, brokkoli)

#### Vitamin B1
- **Important for:**
  * nerve function
  * converting glucose into energy
- **Sources:**
  * nuts
  * seeds
  * whole grains
  
#### Vitamin B2
- **Important for:**
  * nerve function
  * skin
  * converting glucose into energy
- **Sources:**
  * milk
  * eggs
  * mushrooms

#### Vitamin B3
- **Important for:**
  * nerve function
  * skin
  * converting glucose into energy
- **Sources:**
  * fish
  * eggs
  * wheat flour

#### Vitamin B6
- **Important for:**
  * using and storing energy from carbohydrates and protein in food
  * forming red blood cells
- **Sources:**
  * soy beans
  * oats
  * bananas
  
#### Folate
- **Important for:**
  * forming red blood cells
  * preventing birth defects
- **Sources:**
  * leafy green vegetables (e.g., cabbage, kale, spring greens, spinach)
  * peas
  * chickpeas and kidney beans
  
#### Vitamin B12
- **Important for:**
  * releasing energy from food
  * using folate
  * nervous system
  * forming red blood cells
- **Sources:**
  * meat
  * fish
  * milk
  * eggs
  * fortified breakfast cereal and plant milks

#### Vitamin C
- **Important for:**
  * protecting cells
  * wound healing
  * healthy skin, hair, bloos vessels & bones
- **Sources:**
  * citrus fruits
  * berries
  * brokkoli
  * potatoes
  * brussel sprouts
  
#### Vitamin D
- **Important for:**
  * healthy teeth, bones and muscles
- **Sources:**
  * oily fish – such as salmon, sardines, herring and mackerel
  * red meat
  * egg yolk

#### Vitamin E
- **Important for:**
  * healthy teeth, bones and muscles
- **Sources:**
  * plant oils - such as sunflower, soya, corn and olive
  * nuts and seeds
  * wheatgerm – found in cereals and cereal product

#### Calcium
- **Important for:**
  * healthy teeth and bones
  * regulating muscle contractions
  * normal blood clotting
- **Sources:**
  * dairy foods
  * green leafy vegetables
  * fortified foods (e.g., soy milk, wheat products)

#### Copper
- **Important for:**
  * producing red and white blood cells
  * releaasing iron to form haemoglobin
- **Sources:**
  * nuts
  * shellfish

#### Iodine
- **Important for:**
  * producing thyroid hormones
  * maintaining healthy metabolic rate
- **Sources:**
  * fish
  * dairy products
  * eggs

#### Iron
- **Important for:**
  * producing red blood cells
- **Sources:**
  * nuts
  * dried fruit
  * beans (e.g., chickpea, edamame, kidney)
  * red meat

#### Magnesium
- **Important for:**
  * converting food into energy
  * healthy bones
- **Sources:**
  * spinach
  * nuts
  * wholemeal bread

#### Potassium
- **Important for:**
  * control fluid balance
  * healthy heart functioning
- **Sources:**
  * bananas
  * nuts and seeds
  * beans

#### Phosphorus
- **Important for:**
  * bones and teeth
  * releasing energy from foods
- **Sources:**
  * bread
  * brown rice
  * oats
  * dairy products
  
#### Selenium
- **Important for:**
  * immune system
  * reproduction
  * preventing tissue and cell damage
- **Sources:**
  * brazil nuts
  * fish
  * eggs
  * meat

#### Zinc
- **Important for:**
  * making new cells and enzymes
  * processing carbohydrates, proteins and fat from food
  * wound healing
- **Sources:**
  * bread
  * cereal foods (e.g., wheatgerm)
  * dairy products
